### 2015-12-10 paper/5-related-work.tex
Added small mention that CD++ works using distributed simulation, which is not necessarily better

In terms of code design and philosophy, dxex is most related to PythonPDEVS~\cite{PythonPDEVS}.
Performance of PythonPDEVS was still decent, through the use of simulation and activity hints from the modeller.
This allowed the kernel to optimize its internal data structures and algorithms for the specific model being executed.
All changes were completely transparant to the model itself, and were completely optional.
In this spirit, we now offer users the possibility to chose between different synchronization protocols.
This allows them to chose for the most appropriate synchronization, depending on the actual model being simulated.
Contrary to PythonPDEVS, however, dxex doesn't support activity hints.

@@

Previous \textsf{DEVS} simulation tools have already implemented multiple synchronization protocols, though mostly in an ad-hoc way.
For example CD++~\cite{CD++} has both a conservative (CCD++~\cite{CCD++}) and optimistic (PCD++)~\cite{PCD++}) variant.
Despite the implementation of both, they are different projects entirely, and while they might support a similar set of features, they remain different from each other.
Dxex, on the other hand, is a single project, where switching between different synchronization protocols is as simple as switching any other configuration parameter.

>>>>

In terms of code design and philosophy, dxex is most related to PythonPDEVS~\cite{PythonPDEVS}.
Performance of PythonPDEVS was still decent, through the use of simulation and activity hints from the modeller.
This allowed the kernel to optimize its internal data structures and algorithms for the specific model being executed.
All changes were completely transparant to the model itself, and were completely optional.
In this spirit, we now offer users the possibility to chose between different synchronization protocols.
This allows them to chose for the most appropriate synchronization, depending on the actual model being simulated.
Contrary to PythonPDEVS, however, dxex doesn't support model migrations~\cite{PythonPDEVS2} or activity hints~\cite{PythonPDEVS_ACTIMS}.

@@

Previous \textsf{DEVS} simulation tools have already implemented multiple synchronization protocols, though mostly in an ad-hoc way.
For example CD++~\cite{CD++} has both a conservative (CCD++~\cite{CCD++}) and optimistic (PCD++)~\cite{PCD++}) variant.
Despite the implementation of both, they are different projects entirely, and while they might support a similar set of features, they remain different from each other.
Dxex, on the other hand, is a single project, where switching between different synchronization protocols is as simple as switching any other configuration parameter.
CD++, however, implements both conservative and optimistic synchronization for distributed simulation, whereas we limit ourself to parallel simulation.
By limiting our approach to parallel simulation, we are able to achieve higher speedups through the use of shared memory communication.
